Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-07-19 Submission.Rmd
gutting results

>Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.

@@

library(ggplot2)
#ggplot(resource, aes(x=sd)) + geom_histogram()
ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .)

@@

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers. The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).

@@

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items. Here, the Figure \@ref(fig:combinegraphs) discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation. Taken with the Figure \@ref(fig:scalelevelgraphs) takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.

@@

library("gridExtra")
grid.arrange(a, b, ncol = 2, nrow = 1)

@@

```
We next explored whether there was statistical support for the hypothesis that the relationship between the challenge stressors and outcomes (i.e., engagement, stress, and burnout) were moderated by resources. In order to test for the presence of an interactive effect, a series of hierarchical regressions were conducted with challenge stressors and resources added in step one of the model and an interaction term, challenge stressors*resources, added in step two of the model.

@@

Table \@ref(tab:chal-resource-table) summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`. H3A predicted that both resources and challenges would predict engagement. Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation. Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge stressors and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_stress_anova$Df[2]`, `r cr_stress_anova$Res.Df[2]`) = `r cr_stress_anova$F[2]`, and thus does not support the presence of moderation.

Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_burn_m2)$adj.r.squared, 2)`, `r cr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`,  and thus failing to provide statistical support for the presence of moderation. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.

@@

papaja::apa_table(regtable,
                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")
```

We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model. See Table \@ref(tab:hind-resource-table).

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`. An interaction between hindrances and resources was not found.

Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, $R^2$ = `r round(summary(hr_stress_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_stress_m2)$adj.r.squared, 2)`, `r hr_stress_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_stress_r_square_change`, $\Delta F$ (`r hr_stress_anova$Df[2]`, `r hr_stress_anova$Res.Df[2]`) = `r hr_stress_anova$F[2]`, supporting the presence of a moderated effect.  See Figure \@ref(fig:hind-resource-stress-int). As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect. Again, see Figure \@ref(fig:hind-resource-burn-int). As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.

Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance stressors and the outcomes of strain and burnout.

@@

In addition to the two hypotheses, two sets of exploratory analyses were also pursued: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands? To answer these questions, authors first categorized O\*Net items into the elements listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O\*Net item is, “How much decision making freedom, without supervision, does your job offer?”. This O\*Net item was retained within the "autonomy" category. Mean ratings of the O\*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.

Figure \@ref(fig:scalelevelgraphs) presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).  First exploring the right side of Figure \@ref(fig:scalelevelgraphs), there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control). As described above, the left side of Figure \@ref(fig:scalelevelgraphs) shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.

Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \@ref(fig:scalelevelgraphs). The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for Participation was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for Autonomy was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for Team Cohesion was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`). Statistical significance was less than .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure \@ref(fig:scalelevelgraphs)). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories. In fact, the means were nearly identical for resource and challenge ratings for all for categories. The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.

Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure \@ref(fig:scalelevelgraphs)). The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F` ($\eta^2$ was `r report1$ANOVA$pes`). The effect for Physical Environment was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`). The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`). The effect for Emotional Demands was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for Recipient Contact was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`). The effect for Work Pressure was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a *resource* (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the left hand side of Figure \@ref(fig:scalelevelgraphs). In other words, demands are viewed as resources. In sum, these results provide some support for RQ 1 and 2.

>>>>

>Hypothesis 3b: Both challenge and hindrance demands positively predict stress and burnout.

@@

library(ggplot2)
#ggplot(resource, aes(x=sd)) + geom_histogram()
ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .) + labs(x = "Standard Deviation")

@@

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative most and least consistency. Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers. The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).

@@

In addition to highlighting extremely agreed- or disagreed-upon characteristics, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items. Here, discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

@@

library("gridExtra")
#grid.arrange(a, b, ncol = 2, nrow = 1)

@@

```
### Challenges, Resources, and Outcomes

@@

H3A predicted that both resources and challenges would predict engagement. Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout). Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.  Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation (Hypothesis 4a). Figure \@ref(fig:chal-resource-int) illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge demands and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`, failing to provide support for Hypothesis 3b. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_stress_anova$Df[2]`, `r cr_stress_anova$Res.Df[2]`) = `r cr_stress_anova$F[2]`, and thus does not support the presence of moderation.

Finally, challenge demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(cr_burn_m2)$adj.r.squared, 2)`, `r cr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`,  and thus failing to provide statistical support for the presence of moderation (Hypothesis 4a). In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.

@@

papaja::apa_table(regtable,
                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")
```
### Hindrances, Resources, and Outcomes

We also explored whether there was an interaction between hindrance demands and resources on the outcome variables. Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions. First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2` [see Table \@ref(tab:hind-resource-table)]. The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`. An interaction between hindrances and resources was not found.

Next exploring stress, hindrance demands and resources explained a statistically significant amount of the variability in stress, $R^2$ = `r round(summary(hr_stress_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_stress_m2)$adj.r.squared, 2)`, `r hr_stress_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_stress_r_square_change`, $\Delta F$ (`r hr_stress_anova$Df[2]`, `r hr_stress_anova$Res.Df[2]`) = `r hr_stress_anova$F[2]`, supporting the presence of a moderated effect.  See Figure \@ref(fig:hind-resource-stress-int). As expected, the relationship between hindrance demands and strain becomes weaker as workers perceive more resources.

Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect [see Figure \@ref(fig:hind-resource-burn-int)]. As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources. Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.

@@
